---
title: "Tech 5. Multiverse/Dredge"
output: html_document
---


This code has two purposes. 

The first is to determine how much variance we should reasonably expect to explain using a 'static' multiverse approach where we use a single worked up data set from one of the teams and then apply a range of possible model specifications to it. Then we predict the outcomes using the model specifications. 

The second is to run a multiverse analysis of the real data and real model specifications to see if we 'missed' anything or combinations of things that could explain the outcomes.

```{r setup, include=FALSE}
rm(list = ls())
library(pacman)

options(scipen = 999)

pacman::p_load("ggplot2","tidyverse","MuMIn","ggpubr","ragg","factoextra","lme4","dplyr","lmerTest","margins")

```

## Expected Explained Variance (a simulation)

We take a team whose results were derived using R and used three waves of the ISSP - Team 18. Their DV is dichotomized, the has pluses and minuses in our multiverse analysis.

```{r team18_sim, warning = F, message = F}
t18m <- read.csv(file = here::here("data/team18_multi.csv"), header = T)

# doesn't include all macro-indicators, merge in here
cri_macro <- read.csv(file = here::here("data/cri_macro.csv"), header = T)

# merge on country
t18m <- left_join(t18m, cri_macro, by = c("iso_country","year"))

# make numeric
t18m <- t18m %>%
    mutate(wdi_unempilo = as.numeric(wdi_unempilo),
           socx_oecd = as.numeric(socx_oecd),
           gdp_oecd = as.numeric(gdp_oecd),
           ginid_solt = as.numeric(ginid_solt),
           migstock_un = as.numeric(migstock_un),
           netmigpct = as.numeric(netmigpct)) %>%
    dplyr::select(., year, female:health_c, migstock_un, netmigpct, wdi_unempilo, socx_oecd, gdp_oecd, iso_country)


```

## Data Frame Prep

```{r models}
dvs <- c("jobs","unemployed","reduce_income_diff","old_age_care","housing","health")

dvs_c <- c("jobs_c","unemp_c","incdiff_c","oldage_c","housing_c","health_c")

# for stock effects
vars <- c("", "wdi_unempilo + ", "socx_oecd + ", "gdp_oecd + ", "netmigpct + ", 
          "wdi_unempilo + socx_oecd + ", 
          "wdi_unempilo + gdp_oecd + ", 
          "wdi_unempilo + socx_oecd + gdp_oecd + ", 
          "socx_oecd + gdp_oecd + ", 
          "netmigpct + wdi_unempilo + ", 
          "netmigpct + socx_oecd + ", 
          "netmigpct + gdp_oecd + ", 
          "netmigpct + wdi_unempilo + socx_oecd + ", 
          "netmigpct + wdi_unempilo + gdp_oecd + ", 
          "netmigpct + socx_oecd + gdp_oecd + ", 
          "netmigpct + wdi_unempilo + socx_oecd + gdp_oecd + ")

# switch stock and flow for flow effects
vars2 <- c("", "wdi_unempilo + ", "socx_oecd + ", "gdp_oecd + ", "migstock_un + ", 
          "wdi_unempilo + socx_oecd + ", 
          "wdi_unempilo + gdp_oecd + ", 
          "wdi_unempilo + socx_oecd + gdp_oecd + ", 
          "socx_oecd + gdp_oecd + ", 
          "migstock_un + wdi_unempilo + ", 
          "migstock_un + socx_oecd + ", 
          "migstock_un + gdp_oecd + ", 
          "migstock_un + wdi_unempilo + socx_oecd + ", 
          "migstock_un + wdi_unempilo + gdp_oecd + ", 
          "migstock_un + socx_oecd + gdp_oecd + ", 
          "migstock_un + wdi_unempilo + socx_oecd + gdp_oecd + ")

# names(vars) <- c(1:16)

# create a results frame
m1_results <- matrix(ncol = 17, nrow = 576)
m2_results <- matrix(ncol = 17, nrow = 576)
m3_results <- matrix(ncol = 17, nrow = 576)
m4_results <- matrix(ncol = 17, nrow = 576)

colnames(m1_results) <- c("mname", "dv","AME", "p", "mator", "sample", "unemp", "socx", "gdp", "stock", "netmig", "AME_type", "twowayfe", "ctry_dummies","year_dummies","glm","logit")
colnames(m2_results) <- colnames(m1_results)
colnames(m3_results) <- colnames(m1_results)
colnames(m4_results) <- colnames(m1_results)


```

## OLS Models

### Stock Models, OLS, All years
```{r models}
i = 1
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m, na.action = "na.omit")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m1_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m1_results[i,5:6] <- c("ols","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,10] <- 1
m1_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,12:17] <- c("Stock",1,0,0,0,0)
i <- i + 1
    }
}
```

### Net Models, OLS, All years
```{r models2}
i = 97
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m, na.action = "na.omit")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m1_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m1_results[i,5:6] <- c("ols","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,11] <- 1
m1_results[i,12:17] <- c("Flow",1,0,0,0,0)
i <- i + 1
    }
}
```

### Stock Models, OLS, 1996 & 2006 only
```{r models3}
t18m_9606 <- subset(t18m, year != 2016)

i = 1
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- lm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m_9606, na.action = "na.omit")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m2_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m2_results[i,5:6] <- c("ols","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,10] <- 1
m2_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,12:17] <- c("Stock",1,0,0,0,0)
i <- i + 1
    }
}
```



### Net Models, OLS, 1996 & 2006 only
```{r models4}

i = 97
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- lm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m_9606, na.action = "na.omit")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m2_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m2_results[i,5:6] <- c("ols","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,11] <- 1
m2_results[i,12:17] <- c("Flow",1,0,0,0,0)
i <- i + 1
    }
}
```

### Stock Models, OLS, 2006 & 2016 only
```{r models3}
t18m_0616 <- subset(t18m, year != 1996)

i = 1
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- lm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m_0616, na.action = "na.omit")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m3_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m3_results[i,5:6] <- c("ols","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,10] <- 1
m3_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,12:17] <- c("Stock",1,0,0,0,0)
i <- i + 1
    }
}
```

### Net Models, OLS, 1996 & 2006 only
```{r models4}

i = 97
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- lm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m_0616, na.action = "na.omit")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m3_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m3_results[i,5:6] <- c("ols","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,11] <- 1
m3_results[i,12:17] <- c("Flow",1,0,0,0,0)
i <- i + 1
    }
}
```


### Stock Models, OLS, All years, Year dummies only (no country FE)
```{r models}
i = 1
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year)"), data = t18m, na.action = "na.omit")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m4_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m4_results[i,5:6] <- c("ols","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,10] <- 1
m4_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,12:17] <- c("Stock",0,0,1,0,0)
i <- i + 1
    }
}
```

### Net Models, OLS, All years, Year dummies only (no country FE)
```{r models2}
i = 97
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year)"), data = t18m, na.action = "na.omit")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m4_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m4_results[i,5:6] <- c("ols","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,11] <- 1
m4_results[i,12:17] <- c("Flow",0,0,1,0,0)
i <- i + 1
    }
}
```

## Logit Models

### Stock Models, logit, All years
```{r models}
i = 385
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- glm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m, na.action = "na.omit", family = "binomial")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("migstock_un")))[2]),5)
m1_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m1_results[i,5:6] <- c("logit","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,10] <- 1
m1_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,12:17] <- c("Stock",1,0,0,0,1)
i <- i + 1
    }
}
```

### Net Models, logit, All years
```{r models2}
i = 481
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- glm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m, na.action = "na.omit", family = "binomial")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("netmigpct")))[2]),5)
m1_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m1_results[i,5:6] <- c("logit","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,11] <- 1
m1_results[i,12:17] <- c("Flow",1,0,0,0,1)
i <- i + 1
    }
}
```

### Stock Models, logit, 1996 & 2006 only
```{r models3}
t18m_9606 <- subset(t18m, year != 2016)

i = 385
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- glm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m_9606, na.action = "na.omit", family = "binomial")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("migstock_un")))[2]),5)
m2_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m2_results[i,5:6] <- c("logit","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,10] <- 1
m2_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,12:17] <- c("Stock",1,0,0,0,1)
i <- i + 1
    }
}
```



### Net Models, logit, 1996 & 2006 only
```{r models4}

i = 481
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- glm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m_9606, na.action = "na.omit", family = "binomial")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("netmigpct")))[2]),5)
m2_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m2_results[i,5:6] <- c("logit","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,11] <- 1
m2_results[i,12:17] <- c("Flow",1,0,0,0,1)
i <- i + 1
    }
}
```

### Stock Models, logit, 2006 & 2016 only
```{r models3}
t18m_0616 <- subset(t18m, year != 1996)

i = 385
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- glm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m_0616, na.action = "na.omit", family = "binomial")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("migstock_un")))[2]),5)
m3_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m3_results[i,5:6] <- c("logit","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,10] <- 1
m3_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,12:17] <- c("Stock",1,0,0,0,1)
i <- i + 1
    }
}
```

### Net Models, logit, 1996 & 2006 only
```{r models4}

i = 481
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- glm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m_0616, na.action = "na.omit", family = "binomial")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("netmigpct")))[2]),5)
m3_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m3_results[i,5:6] <- c("logit","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,11] <- 1
m3_results[i,12:17] <- c("Flow",1,0,0,0,1)
i <- i + 1
    }
}
```


### Stock Models, logit, All years, Year dummies only (no country FE)
```{r models}
i = 385
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- glm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year)"), data = t18m, na.action = "na.omit", family = "binomial")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("migstock_un")))[2]),5)
m4_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m4_results[i,5:6] <- c("logit","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,10] <- 1
m4_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,12:17] <- c("Stock",0,0,1,0,1)
i <- i + 1
    }
}
```

### Net Models, logit, All years, Year dummies only (no country FE)
```{r models2}
i = 481
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- glm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year)"), data = t18m, na.action = "na.omit", family = "binomial")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("netmigpct")))[2]),5)
m4_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m4_results[i,5:6] <- c("logit","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,11] <- 1
m4_results[i,12:17] <- c("Flow",0,0,1,0,1)
i <- i + 1
    }
}
```


## GLM Models

### Stock Models, GLM, All years, country-level, year dummy
```{r models}
i = 193
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lmer(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + (1|iso_country)"), data = t18m, na.action = "na.omit")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m1_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m1_results[i,5:6] <- c("glm","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,10] <- 1
m1_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m1_results[i,12:17] <- c("Stock",0,0,1,1,0)
i <- i + 1
    }
}
```

### Net Models, GLM, All years, country-level, year dummy
```{r models2}
i = 289
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lmer(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + (1 | iso_country)"), data = t18m, na.action = "na.omit")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m1_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m1_results[i,5:6] <- c("glm","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m1_results[i,11] <- 1
m1_results[i,12:17] <- c("Flow",0,0,1,1,0)
i <- i + 1
    }
}
```

### Stock Models, GLM, country-level, year dummy, 1996 & 2006 only
```{r models3}
t18m_9606 <- subset(t18m, year != 2016)

i = 193
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- lmer(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + (1 | iso_country)"), data = t18m_9606, na.action = "na.omit")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m2_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m2_results[i,5:6] <- c("glm","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,10] <- 1
m2_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m2_results[i,12:17] <- c("Stock",0,0,1,1,0)
i <- i + 1
    }
}
```

### Net Models, GLM, country-level, year dummy, 1996 & 2006 only
```{r models4}

i = 289
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- lmer(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + (1 | iso_country)"), data = t18m_9606, na.action = "na.omit")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m2_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m2_results[i,5:6] <- c("glm","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m2_results[i,11] <- 1
m2_results[i,12:17] <- c("Flow",0,0,1,1,0)
i <- i + 1
    }
}
```

### Stock Models, GLM, country-level, year dummy, 2006 & 2016 only
```{r models3}
t18m_0616 <- subset(t18m, year != 1996)

i = 193
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- lmer(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + (1 | iso_country)"), data = t18m_0616, na.action = "na.omit")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m3_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m3_results[i,5:6] <- c("glm","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,10] <- 1
m3_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m3_results[i,12:17] <- c("Stock",0,0,1,1,0)
i <- i + 1
    }
}
```

### Net Models, GLM, country-level, year dummy, 2006 & 2016 only
```{r models4}

i = 289
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- lmer(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + (1 | iso_country)"), data = t18m_0616, na.action = "na.omit")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m3_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m3_results[i,5:6] <- c("glm","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m3_results[i,11] <- 1
m3_results[i,12:17] <- c("Flow",0,0,1,1,0)
i <- i + 1
    }
}
```


### Stock Models, GLM, All years, no year dummy
```{r models}
i = 193
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lmer(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "(1 | iso_country)"), data = t18m, na.action = "na.omit")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m4_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m4_results[i,5:6] <- c("glm","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,10] <- 1
m4_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = T) == TRUE, 1, 0)
m4_results[i,12:17] <- c("Stock",0,0,0,1,0)
i <- i + 1
    }
}
```

### Net Models, GLM, All years, no year dummy
```{r models2}
i = 289
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lmer(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "(1 | iso_country)"), data = t18m, na.action = "na.omit")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m4_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m4_results[i,5:6] <- c("glm","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = T) == TRUE, 1, 0)
m4_results[i,11] <- 1
m4_results[i,12:17] <- c("Flow",0,0,0,1,0)
i <- i + 1
    }
}
```

## Explaining Variance in Multiverse

```{r dataprep}
multi_df <- as.data.frame(rbind(m1_results, m2_results, m3_results, m4_results))

multi_df <- multi_df %>%
    mutate(ols = ifelse(mator == "ols", 1, 0),
           sample = factor(sample),
           otherdv = ifelse(stock == 1 & netmig == 1, 1, 0),
           AME = as.numeric(AME))

save(multi_df, file = here::here("results/multi_df.Rda"))

```


```{r multimodels}

load(file = here::here("results/multi_df.Rda"))


# m0 <- lm(AME ~ 1, data = multi_df)
m1 <- lm(AME ~ factor(dv) + factor(AME_type), data = multi_df)
m2 <- lm(AME ~ factor(dv) + factor(AME_type) + factor(sample), data = multi_df)
m3 <- lm(AME ~ factor(dv) + factor(AME_type) + factor(sample) + unemp + socx + gdp + otherdv, data = multi_df)
m4 <- lm(AME ~ factor(dv) + factor(AME_type) + factor(sample) + unemp + socx + gdp + otherdv + factor(mator), data = multi_df)
m5 <- lm(AME ~ factor(dv) + factor(AME_type) + factor(dv)*factor(AME_type) + factor(sample) + unemp + socx + gdp + otherdv + factor(mator), data = multi_df)

expvar <- matrix(nrow = 5, ncol = 3)

expvar[,1] <- c("m1","m2","m3","m4","m5")
expvar[,2] <- c("DVs + AME type","+ sample", "+ IVs", "+ other DV + Estimator", "DV*Type interaction")
expvar[,3] <- c(summary(m1)[["r.squared"]], summary(m2)[["r.squared"]], summary(m3)[["r.squared"]], summary(m4)[["r.squared"]], summary(m5)[["r.squared"]])

write.csv(expvar, file = "results/TblSX_multi.csv")
```

```{r}
sjPlot::tab_model(m3, m4, m5, show.ci = F, p.style = "stars")
```

