---
title: "Tech 5, Main Analyses"
output: html_notebook
---

This package is needed
http://www.alexlishinski.com/post/2018-04-13-lavaanplot0.5/

   

```{r setup, include=FALSE, warning=F}
rm(list = ls())
library(pacman)

# devtools::install_github("alishinski/lavaanPlot")

pacman::p_load("ggplot2","dplyr","readr","plotscale","lattice","tidyr","readxl","mlogit","jtools","sjPlot","sjmisc","sjlabelled","knitr","kableExtra","lavaan","reshape2","semPlot","lavaanPlot","leaps")



# Column no missing function
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
```

## Data Prep

These datasets were worked up from the file 01_CRI_Data_Prep.Rmd. 

cri = numerical values
cri_str = string values
cri_team = team-level data (by conclusion)
cri_team_combine = team-level data parsed by type of test variable (stock and flow)
cri_indiv = participant-level data from our survey, identifying characteristics redacted

### Load Data

```{r load, warning=F,message=F}
cri <- read.csv(file = "data/cri.csv", header = T)
cri_str <- read.csv(file = "data/cri_str.csv", header = T)
cri_team <- read.csv(file = "data/cri_team_combine.csv", header = T)
cri_indiv <- read.csv(file = "data/cri_indv.csv", header = T)

# cri_team_combine
```






# Regresssion Approach to Explaining Variance

## Explaining Average Marginal Effects

### Model Specifications 

#### DV Type

```{r m1, include = TRUE, warning = F}


#DVs only
m1a <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri)
m1b <- lm(p ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri)
m1c <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale + p, data = cri)

tab_model(m1a,m1b,m1c, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))


```

#### Test IV Type - unweighted

These results do not take into account the varying number of models per team

```{r m1_ivsplit, include = TRUE, warning = F}

cri_stock <- subset(cri, cri$Stock == 1)
cri_flow <- subset(cri, cri$Flow == 1)

#Stock models
m1a_stock <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_stock)
m1b_stock <- lm(p ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_stock)
m1c_stock <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale + p, data = cri_stock)

#Flow models
m1a_flow <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_flow)
m1b_flow <- lm(p ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_flow)
m1c_flow <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale + p, data = cri_flow)

tab_model(m1a_stock,m1b_stock,m1c_stock,m1a_flow,m1b_flow,m1c_flow, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))


```

#### Test IV Type - weighted

We abandon estimation of p-values here. They do not seem to be of substantive interest for us... yet.

Weighting does not improve explained variance.

```{r m1_weight, include = TRUE}

m1aw <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri, weight = (inv_weight/1)*112)
m1aw_stock <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_stock, weights = (inv_weight/1)*112)
m1aw_flow <- lm(AME_Z ~ Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_flow, weights = (inv_weight/1)*112)


tab_model(m1aw,m1aw_stock,m1aw_flow, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))


```

#### Pooled by Test Type

```{r m2_pooled_iv_type}

# Pooled by test variable, ref = change in flow

m2 <- lm(AME_Z ~ factor(main_IV_type), data = cri)

tab_model(m2, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))

```

#### Waves of Data Used

##### Model Specifications - testing universe of wave combinations

Results suggest that using a 2006*2016 interaction 'maximizes' explained variance at 0.008.It suggests leaving out the main effect for w2016, but this is substantively awkward, so we put it back in for the final regression in the next code chunk.

```{r wave_test}

# the use of 1985 and 1990 is quite rare so we focus on the latter three waves as potential interactions
m_wave <-
    regsubsets(AME_Z ~ w1985 + w1990 + w1996 + w2006 + w2016 + w1996*w2006 + w1996*w2016 + w1996*w2006*w2016 + w2006*w2016,
               data = cri,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

plot(m_wave, scale = "adjr2", main = "Adjusted R^2")
```

##### Sample Selection Waves

```{r m3}
m3 <- lm(AME_Z ~ w2006 + w2016 + w2006*w2016, data = cri)
m3_stock <- lm(AME_Z ~ w2006 + w2016 + w2006*w2016, data = cri_stock)
m3_flow <- lm(AME_Z ~ w1996 + w2006 + w2016 + w2006*w2016, data = cri_flow)

tab_model(m3, m3_stock, m3_flow, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))
```


#### Sample Selection Related IVs

##### Universe approach

After running this, it is not even worth modeling. We can only get up to Adj r^2 around 0.01.

```{r sample_test}

# we do not interact all variables because they are mostly mutually exclusive 
m_sample <-
    regsubsets(AME_Z ~ w2006 + w2016 + w2006*w2016 + orig13 + orig17 + eeurope + allavailable + w2016*orig13 + w2016*orig17 + w2016*eeurope + w2016*allavailable + w2006*w2016*orig13 + w2006*w2016*orig17 + w2006*w2016*eeurope + w2006*w2016*allavailable + w2006*w2016*orig13 + w2006*orig13 + w2006*orig17 + w2006*eeurope + w2006*allavailable,
               data = cri,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

plot(m_sample, scale = "adjr2", main = "Adjusted R^2")
```

##### Sample selection

orig13
orig17, dropped, see above
eeurope
allavailable



```{r m4}
m4 <- lm(AME_Z ~ orig13  + eeurope + allavailable + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable, data = cri)
m4_stock <- lm(AME_Z ~ orig13  + eeurope + allavailable + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable, data = cri_stock)
m4_flow <- lm(AME_Z ~ orig13  + eeurope + allavailable + + w1996 + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable, data = cri_flow)

tab_model(m4, m4_stock, m4_flow, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))

```


### Team Qualities


*belief_ipred* - Belief that Hypothesis is true (that immigration reduces support), team average of predicted factor scores
*pro_immigrant* - Support laws to better integrate immigrants, team average, single question
*topic_ipred* - Knowledge and experience with the topic of immigration and welfare state preferences, team average of predicted factor scores
*stats_ipred* - Knowledge and experience with quantiative statistical analysis, team average of predicted factor scores
*total_score* - Average score of each model from subjective voting amongst participants, each participant reviewed 3 to 4 models

#### Correlations

```{r rq_corr}
cor_rq <- select(cri, AME_Z, Hsup, AME_sup_p05, belief_ipred, pro_immigrant, topic_ipred, stats_ipred, total_score)
# cor_rq <- completeFun(cor_rq, c("AME_Z", "belief_ipred"))
# cor_rq <- as.data.frame(cor_rq)
cor_rqa <- as.data.frame(round(cor(cor_rq, use = "pairwise.complete.obs"), 3))

# Start to build main findings table
cor_rqa <- as.data.frame(cor_rqa[4:8,1:3])
cor_rqa2 <- round(100*(cor_rqa^2), 3)

# Stock and Flow only
cor_rq_stock <- select(cri_stock, AME_Z, belief_ipred, pro_immigrant, topic_ipred, stats_ipred, total_score)
cor_rqa_stock <- as.data.frame(round(cor(cor_rq_stock, use = "pairwise.complete.obs"), 3))

cor_rqa_stock <- as.data.frame(cor_rqa_stock[2:6,1])
cor_rqa2_stock <- round(100*(cor_rqa_stock^2), 3)

cor_rq_flow <- select(cri_flow, AME_Z, belief_ipred, pro_immigrant, topic_ipred, stats_ipred, total_score)
cor_rqa_flow <- as.data.frame(round(cor(cor_rq_flow, use = "pairwise.complete.obs"), 3))

cor_rqa_flow <- as.data.frame(cor_rqa_flow[2:6,1])
cor_rqa2_flow <- round(100*(cor_rqa_flow^2), 3)

# bind all together

cor_rqa21 <- as.data.frame(cor_rqa2[,1])
cor_rqa22 <- as.data.frame(cor_rqa2[,2:3])
cor_rq_final <- bind_cols(cor_rqa21, cor_rqa2_stock, cor_rqa2_flow, cor_rqa22)

rm(cor_rq, cor_rq_flow, cor_rq_stock, cor_rqa, cor_rqa_flow, cor_rqa_stock, cor_rqa2, cor_rqa2_flow, cor_rqa2_stock)
```


#### Universe Approach

```{r qs_test}

# we do not interact all variables because they are mostly mutually exclusive 
m_qs <-
    regsubsets(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*pro_immigrant + belief_ipred*topic_ipred + belief_ipred*stats_ipred + belief_ipred*total_score + pro_immigrant*topic_ipred + pro_immigrant*stats_ipred + pro_immigrant*total_score + topic_ipred*stats_ipred + topic_ipred*total_score + stats_ipred*total_score,
               data = cri,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

plot(m_qs, scale = "adjr2", main = "Adjusted R^2")
```

```{r m20}
m20 <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred, data = cri)
m20_stock <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred, data = cri_stock)
m20_flow <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred, data = cri_flow)

tab_model(m20, m20_stock, m20_flow, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))

```


### All Aspects Combined


```{r m30}
m30 <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred + orig13  + eeurope + allavailable + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable + Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri)

m30_stock <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred + orig13  + eeurope + allavailable + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable + Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_stock)

m30_flow <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred + orig13  + eeurope + allavailable + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable + Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_flow)

tab_model(m30, m30_stock, m30_flow, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))
```


### All Aspects Combined Weighted


```{r m30w}
m30_w <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred + orig13  + eeurope + allavailable + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable + Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri, weights = (inv_weight/1)*112)

m30_stock_w <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred + orig13  + eeurope + allavailable + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable + Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_stock, weights = (inv_weight/1)*112)

m30_flow_w <- lm(AME_Z ~ belief_ipred + pro_immigrant + topic_ipred + stats_ipred + total_score + belief_ipred*topic_ipred + belief_ipred*stats_ipred + pro_immigrant*stats_ipred + topic_ipred*stats_ipred + orig13  + eeurope + allavailable + w2006 + w2016 + w2006*w2016 + w2016*eeurope + w2016*allavailable + Jobs + Unemp + IncDiff + OldAge + House + Health + Scale, data = cri_flow, weights = (inv_weight/1)*112)

tab_model(m30, m30_stock, m30_flow, p.style = "stars", show.ci = F, rm.terms = c("(Intercept)"))
```

###
