---
title: "06. Multiverse/Dredge"
output: html_document
---

This code has two purposes. 

The first is to determine how much variance we should reasonably expect to explain using a 'static' multiverse approach where we use a single worked up data set from one of the teams and then apply a range of possible model specifications to it. Then we predict the outcomes using the model specifications. 

The second is to run a multiverse analysis of the real data and real model specifications to see if we 'missed' anything or combinations of things that could explain the outcomes.

```{r setup, include=FALSE}
library("pacman")

options(scipen = 999)

pacman::p_load("ggplot2","tidyverse","MuMIn","ggpubr","ragg","factoextra","lme4","dplyr","lmerTest","margins","rvest","nnet")
```

## Expected Explained Variance (a simulation)

We take a team whose results were derived using R and used three waves of the ISSP - Team 18. Their DV is dichotomized, the has pluses and minuses in our multiverse analysis.

```{r team18_sim, warning = FALSE, message = FALSE}
t18m <- read.csv(file = here::here("data/team18_multi.csv"), header = TRUE)

# doesn't include all macro-indicators, merge in here
cri_macro <- read.csv(file = here::here("data/cri_macro.csv"), header = TRUE)

# merge on country
t18m <- left_join(t18m, cri_macro, by = c("iso_country","year"))

# make numeric
t18m <- t18m %>%
    mutate(wdi_unempilo = as.numeric(wdi_unempilo),
           socx_oecd = as.numeric(socx_oecd),
           gdp_oecd = as.numeric(gdp_oecd),
           ginid_solt = as.numeric(ginid_solt),
           migstock_un = as.numeric(migstock_un),
           netmigpct = as.numeric(netmigpct)) %>%
    dplyr::select(., year, female:health_c, migstock_un, netmigpct, wdi_unempilo, socx_oecd, gdp_oecd, iso_country)
```

### Data Frame Prep

```{r models, warning = FALSE}
dvs <- c("jobs","unemployed","reduce_income_diff","old_age_care","housing","health")

dvs_c <- c("jobs_c","unemp_c","incdiff_c","oldage_c","housing_c","health_c")

# for stock effects
vars <- c("", "wdi_unempilo + ", "socx_oecd + ", "gdp_oecd + ", "netmigpct + ", 
          "wdi_unempilo + socx_oecd + ", 
          "wdi_unempilo + gdp_oecd + ", 
          "wdi_unempilo + socx_oecd + gdp_oecd + ", 
          "socx_oecd + gdp_oecd + ", 
          "netmigpct + wdi_unempilo + ", 
          "netmigpct + socx_oecd + ", 
          "netmigpct + gdp_oecd + ", 
          "netmigpct + wdi_unempilo + socx_oecd + ", 
          "netmigpct + wdi_unempilo + gdp_oecd + ", 
          "netmigpct + socx_oecd + gdp_oecd + ", 
          "netmigpct + wdi_unempilo + socx_oecd + gdp_oecd + ")

# switch stock and flow for flow effects
vars2 <- c("", "wdi_unempilo + ", "socx_oecd + ", "gdp_oecd + ", "migstock_un + ", 
          "wdi_unempilo + socx_oecd + ", 
          "wdi_unempilo + gdp_oecd + ", 
          "wdi_unempilo + socx_oecd + gdp_oecd + ", 
          "socx_oecd + gdp_oecd + ", 
          "migstock_un + wdi_unempilo + ", 
          "migstock_un + socx_oecd + ", 
          "migstock_un + gdp_oecd + ", 
          "migstock_un + wdi_unempilo + socx_oecd + ", 
          "migstock_un + wdi_unempilo + gdp_oecd + ", 
          "migstock_un + socx_oecd + gdp_oecd + ", 
          "migstock_un + wdi_unempilo + socx_oecd + gdp_oecd + ")

# names(vars) <- c(1:16)

# create a results frame
m1_results <- matrix(ncol = 17, nrow = 576)
m2_results <- matrix(ncol = 17, nrow = 576)
m3_results <- matrix(ncol = 17, nrow = 576)
m4_results <- matrix(ncol = 17, nrow = 576)

colnames(m1_results) <- c("mname", "dv","AME", "p", "mator", "sample", "unemp", "socx", "gdp", "stock", "netmig", "AME_type", "twowayfe", "ctry_dummies","year_dummies","glm","logit")
colnames(m2_results) <- colnames(m1_results)
colnames(m3_results) <- colnames(m1_results)
colnames(m4_results) <- colnames(m1_results)
```

## OLS Models

### Stock Models, OLS, All years

```{r models1, warning = FALSE}
i = 1
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m, na.action = "na.omit")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m1_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m1_results[i,5:6] <- c("ols","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,10] <- 1
m1_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,12:17] <- c("Stock",1,0,0,0,0)
i <- i + 1
    }
}
```

### Net Models, OLS, All years

```{r models2, warning = FALSE}
i = 97
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m, na.action = "na.omit")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m1_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m1_results[i,5:6] <- c("ols","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,11] <- 1
m1_results[i,12:17] <- c("Flow",1,0,0,0,0)
i <- i + 1
    }
}
```

### Stock Models, OLS, 1996 & 2006 only

```{r models3, warning = FALSE}
t18m_9606 <- subset(t18m, year != 2016)

i = 1
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- lm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m_9606, na.action = "na.omit")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m2_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m2_results[i,5:6] <- c("ols","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,10] <- 1
m2_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,12:17] <- c("Stock",1,0,0,0,0)
i <- i + 1
    }
}
```

### Net Models, OLS, 1996 & 2006 only

```{r models4, warning = FALSE}

i = 97
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- lm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m_9606, na.action = "na.omit")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m2_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m2_results[i,5:6] <- c("ols","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,11] <- 1
m2_results[i,12:17] <- c("Flow",1,0,0,0,0)
i <- i + 1
    }
}
```

### Stock Models, OLS, 2006 & 2016 only

```{r models5, warning = FALSE}
t18m_0616 <- subset(t18m, year != 1996)

i = 1
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- lm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m_0616, na.action = "na.omit")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m3_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m3_results[i,5:6] <- c("ols","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,10] <- 1
m3_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,12:17] <- c("Stock",1,0,0,0,0)
i <- i + 1
    }
}
```

### Net Models, OLS, 1996 & 2006 only

```{r models6, warning = FALSE}

i = 97
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- lm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m_0616, na.action = "na.omit")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m3_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m3_results[i,5:6] <- c("ols","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,11] <- 1
m3_results[i,12:17] <- c("Flow",1,0,0,0,0)
i <- i + 1
    }
}
```

### Stock Models, OLS, All years, Year dummies only (no country FE)

```{r models7, warning = FALSE}
i = 1
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year)"), data = t18m, na.action = "na.omit")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m4_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m4_results[i,5:6] <- c("ols","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,10] <- 1
m4_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,12:17] <- c("Stock",0,0,1,0,0)
i <- i + 1
    }
}
```

### Net Models, OLS, All years, Year dummies only (no country FE)

```{r models8, warning = FALSE}
i = 97
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year)"), data = t18m, na.action = "na.omit")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m4_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m4_results[i,5:6] <- c("ols","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,11] <- 1
m4_results[i,12:17] <- c("Flow",0,0,1,0,0)
i <- i + 1
    }
}
```

## Logit Models

### Stock Models, logit, All years

```{r model9, warning = FALSE}
i = 385
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- glm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m, na.action = "na.omit", family = "binomial")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("migstock_un")))[2]),5)
m1_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m1_results[i,5:6] <- c("logit","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,10] <- 1
m1_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,12:17] <- c("Stock",1,0,0,0,1)
i <- i + 1
    }
}
```

### Net Models, logit, All years

```{r models10, warning = FALSE}
i = 481
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- glm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m, na.action = "na.omit", family = "binomial")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("netmigpct")))[2]),5)
m1_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m1_results[i,5:6] <- c("logit","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,11] <- 1
m1_results[i,12:17] <- c("Flow",1,0,0,0,1)
i <- i + 1
    }
}
```

### Stock Models, logit, 1996 & 2006 only

```{r models11, warning = FALSE}
t18m_9606 <- subset(t18m, year != 2016)

i = 385
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- glm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m_9606, na.action = "na.omit", family = "binomial")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("migstock_un")))[2]),5)
m2_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m2_results[i,5:6] <- c("logit","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,10] <- 1
m2_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,12:17] <- c("Stock",1,0,0,0,1)
i <- i + 1
    }
}
```

### Net Models, logit, 1996 & 2006 only

```{r models12, warning = FALSE}
i = 481
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- glm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m_9606, na.action = "na.omit", family = "binomial")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("netmigpct")))[2]),5)
m2_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m2_results[i,5:6] <- c("logit","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,11] <- 1
m2_results[i,12:17] <- c("Flow",1,0,0,0,1)
i <- i + 1
    }
}
```

### Stock Models, logit, 2006 & 2016 only

```{r models13, warning = FALSE}
t18m_0616 <- subset(t18m, year != 1996)

i = 385
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- glm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + factor(iso_country)"), data = t18m_0616, na.action = "na.omit", family = "binomial")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("migstock_un")))[2]),5)
m3_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m3_results[i,5:6] <- c("logit","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,10] <- 1
m3_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,12:17] <- c("Stock",1,0,0,0,1)
i <- i + 1
    }
}
```

### Net Models, logit, 1996 & 2006 only

```{r models14, warning = FALSE}
i = 481
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- glm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + factor(iso_country)"), data = t18m_0616, na.action = "na.omit", family = "binomial")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("netmigpct")))[2]),5)
m3_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m3_results[i,5:6] <- c("logit","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,11] <- 1
m3_results[i,12:17] <- c("Flow",1,0,0,0,1)
i <- i + 1
    }
}
```

### Stock Models, logit, All years, Year dummies only (no country FE)

```{r models15, warning = FALSE}
i = 385
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- glm(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year)"), data = t18m, na.action = "na.omit", family = "binomial")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("migstock_un")))[2]),5)
m4_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m4_results[i,5:6] <- c("logit","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,10] <- 1
m4_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,12:17] <- c("Stock",0,0,1,0,1)
i <- i + 1
    }
}
```

### Net Models, logit, All years, Year dummies only (no country FE)

```{r models16, warning = FALSE}
i = 481
for (dv in dvs) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- glm(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year)"), data = t18m, na.action = "na.omit", family = "binomial")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(as.numeric(summary(margins(x, variables = c("netmigpct")))[2]),5)
m4_results[i,4] <- round(summary(x)$coefficients[2,4],5)
m4_results[i,5:6] <- c("logit","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,11] <- 1
m4_results[i,12:17] <- c("Flow",0,0,1,0,1)
i <- i + 1
    }
}
```

## GLM Models

### Stock Models, GLM, All years, country-level, year dummy

```{r models17, warning = FALSE}
i = 193
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lmer(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + (1|iso_country)"), data = t18m, na.action = "na.omit")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m1_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m1_results[i,5:6] <- c("glm","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,10] <- 1
m1_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,12:17] <- c("Stock",0,0,1,1,0)
i <- i + 1
    }
}
```

### Net Models, GLM, All years, country-level, year dummy

```{r models18, warning = FALSE}
i = 289
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lmer(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + (1 | iso_country)"), data = t18m, na.action = "na.omit")
m1_results[i,1] <- model
m1_results[i,2] <- dv
m1_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m1_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m1_results[i,5:6] <- c("glm","All")
m1_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m1_results[i,11] <- 1
m1_results[i,12:17] <- c("Flow",0,0,1,1,0)
i <- i + 1
    }
}
```

### Stock Models, GLM, country-level, year dummy, 1996 & 2006 only

```{r models19, warning = FALSE}
t18m_9606 <- subset(t18m, year != 2016)

i = 193
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- lmer(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + (1 | iso_country)"), data = t18m_9606, na.action = "na.omit")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m2_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m2_results[i,5:6] <- c("glm","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,10] <- 1
m2_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,12:17] <- c("Stock",0,0,1,1,0)
i <- i + 1
    }
}
```

### Net Models, GLM, country-level, year dummy, 1996 & 2006 only

```{r models20, warning = FALSE}
i = 289
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- lmer(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + (1 | iso_country)"), data = t18m_9606, na.action = "na.omit")
m2_results[i,1] <- model
m2_results[i,2] <- dv
m2_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m2_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m2_results[i,5:6] <- c("glm","w96_06")
m2_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m2_results[i,11] <- 1
m2_results[i,12:17] <- c("Flow",0,0,1,1,0)
i <- i + 1
    }
}
```

### Stock Models, GLM, country-level, year dummy, 2006 & 2016 only

```{r models21, warning = FALSE}
t18m_0616 <- subset(t18m, year != 1996)

i = 193
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
y <- vars[var]
x <- lmer(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "factor(year) + (1 | iso_country)"), data = t18m_0616, na.action = "na.omit")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m3_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m3_results[i,5:6] <- c("glm","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,10] <- 1
m3_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,12:17] <- c("Stock",0,0,1,1,0)
i <- i + 1
    }
}
```

### Net Models, GLM, country-level, year dummy, 2006 & 2016 only

```{r models22, warning = FALSE}
i = 289
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars2[var])
y <- vars2[var]
x <- lmer(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "factor(year) + (1 | iso_country)"), data = t18m_0616, na.action = "na.omit")
m3_results[i,1] <- model
m3_results[i,2] <- dv
m3_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m3_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m3_results[i,5:6] <- c("glm","w06_16")
m3_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m3_results[i,11] <- 1
m3_results[i,12:17] <- c("Flow",0,0,1,1,0)
i <- i + 1
    }
}
```

### Stock Models, GLM, All years, no year dummy

```{r models23, warning = FALSE}
i = 193
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lmer(paste0(dv,
               " ~ ",
               "migstock_un + ",
               vars[var], 
               "(1 | iso_country)"), data = t18m, na.action = "na.omit")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m4_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m4_results[i,5:6] <- c("glm","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,10] <- 1
m4_results[i,11] <- ifelse(grepl("netmig",vars[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,12:17] <- c("Stock",0,0,0,1,0)
i <- i + 1
    }
}
```

### Net Models, GLM, All years, no year dummy

```{r models24, warning = FALSE}
i = 289
for (dv in dvs_c) {
    for (var in 1:16) {
model <- paste0("m1_",dv, "_", vars[var])
x <- lmer(paste0(dv,
               " ~ ",
               "netmigpct + ",
               vars2[var], 
               "(1 | iso_country)"), data = t18m, na.action = "na.omit")
m4_results[i,1] <- model
m4_results[i,2] <- dv
m4_results[i,3] <- round(summary(x)$coefficients[2,1],5)
m4_results[i,4] <- round(summary(x)$coefficients[2,5],5)
m4_results[i,5:6] <- c("glm","All")
m4_results[i,7] <- ifelse(grepl("unemp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,8] <- ifelse(grepl("socx",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,9] <- ifelse(grepl("gdp",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,10] <- ifelse(grepl("stock",vars2[var], fixed = TRUE) == TRUE, 1, 0)
m4_results[i,11] <- 1
m4_results[i,12:17] <- c("Flow",0,0,0,1,0)
i <- i + 1
    }
}
```

## Explaining Variance in Multiverse

```{r dataprep, warning = FALSE}
multi_df <- as.data.frame(rbind(m1_results, m2_results, m3_results, m4_results))

multi_df <- multi_df %>%
    mutate(ols = ifelse(mator == "ols", 1, 0),
           sample = factor(sample),
           otherdv = ifelse(stock == 1 & netmig == 1, 1, 0),
           AME = as.numeric(AME))

save(multi_df, file = here::here("results/multi_df.Rda"))
```

```{r multimodels, warning = FALSE}
load(file = here::here("results/multi_df.Rda"))

# m0 <- lm(AME ~ 1, data = multi_df)
m1 <- lm(AME ~ factor(dv) + factor(AME_type), data = multi_df)
m2 <- lm(AME ~ factor(dv) + factor(AME_type) + factor(sample), data = multi_df)
m3 <- lm(AME ~ factor(dv) + factor(AME_type) + factor(sample) + unemp + socx + gdp + otherdv, data = multi_df)
m4 <- lm(AME ~ factor(dv) + factor(AME_type) + factor(sample) + unemp + socx + gdp + otherdv + factor(mator), data = multi_df)
m5 <- lm(AME ~ factor(dv) + factor(AME_type) + factor(dv)*factor(AME_type) + factor(sample) + unemp + socx + gdp + otherdv + factor(mator), data = multi_df)

expvar <- matrix(nrow = 5, ncol = 3)

expvar[,1] <- c("m1","m2","m3","m4","m5")
expvar[,2] <- c("DVs + AME type","+ sample", "+ IVs", "+ other DV + Estimator", "DV*Type interaction")
expvar[,3] <- c(summary(m1)[["r.squared"]], summary(m2)[["r.squared"]], summary(m3)[["r.squared"]], summary(m4)[["r.squared"]], summary(m5)[["r.squared"]])

write.csv(expvar, file = here::here("results/TblS8.csv"))
```

```{r plotms}
sjPlot::tab_model(m3, m4, m5, show.ci = FALSE, p.style = "stars")
```

## Dredge Function

Given computing times, we start with smaller sets of variables and then eliminate those that do not appear in the top fitting models (AIC/LL). 

We also import results from the dredge script to reduce reproduction computing times from [`dredge.R`](../code/script/). 

And for the R&R suggestion of running all interactions from [`dredge_v2.R`](../code/script/)

```{r loaddredge}
load(file = here::here("code/script/dredge.Rdata"))
```


## Final Model

### First Iteration

Used to explain variance reduction - compare with Fig 3 in the main text and Table S6. These variables were selected from iterating dredge.

```{r final, warning = FALSE}
m_dredged <- lmer(AME_Z ~ Jobs + IncDiff + House + Stock + ChangeFlow + Stock*IncDiff + w2016 + orig13 +  eeurope + twowayfe + level_cyear + twowayfe*Jobs + twowayfe*Stock + Jobs*Stock + (1 | team), data = cri_ml)

m_d_out_v <- as.data.frame(VarCorr(m_dredged))

m_d_out <- as.data.frame(read_html(here::here("results/reg_dredge.htm")) %>% html_table(fill=TRUE))

# add var to data frame
m_d_out <- m_d_out[-c(18:21),]
m_d_out[c(15:17),1] <- c("Team-Level","Model-Level","Total")
# values taken from main models, see Table S6
m_d_out[c(15:17),2] <- c(round((-1*(m_d_out_v[1,4]-0.000615)/0.000615)*100,3), 
                         round((-1*(m_d_out_v[2,4]-0.004882)/0.004882)*100,3), 
                         round((((-1*(m_d_out_v[1,4]-0.000615)) + (-1*(m_d_out_v[2,4]-0.004882)))/0.005497)*100,3))

# Save table
write.csv(m_d_out, file = here::here("results/TblS10.csv"))
```

### Reviewer suggested - try all interactions

Here we calculated every interaction pair leading to 5,565 interactions, this was reduced to 2,637 after removing those that had no variance, for example those who used a Bayes estimator did not use OLS so a Bayes\*OLS interaction produced all zeros. We see 7 variables as a maximum for testing the dredge function, again this function runs every combination possible of all 7 variables and all subsets. We tried 10 but too many matricies were rank deficient (more evidence that it is too many variables). The reader may think that more than 7 variables to explain the outcomes is warranted, but **none** of our models showed good fit statistics with more than two interaction variables in the model. Next we had a random seed select sets of 7 variables out of the 2,637 to test. We iterated this 1000 times leading to 1,028,000 models. We then selected the best two fitting models based on AIC from each of the 1000 iterations. From these we extracted all variables used in all those best fitting models. After removing duplicates this resulted in 19 variables. We then re-ran the same process using only these 19 variables and 100 iterations and the best fitting models from these iterations contained 4 variables. In the next code chunk we add these 4 variables to our existing 'best' models to see if they can explain more variance without reducing model fit. We should also point our here that most of these interactions produce unique identifications of team's models (i.e., used by only one team so not fit for putting in a regression although we do it anyway for thoroughness and to make the reviewer happy)

It identified one interaction that could improve fit and explained variance slightly. As this interaction occurs in more than one team, we elect to keep it. 

They are:
(first dredge)
Stock*Jobs
twowayfe*Stock
(second dredge)
cluster_any*gdp_ivC
ols*unbalpanel
Unemp*publice_iv
w1996*conservatism_ivC


```{r dredge_v2}
dredge_v2 <- read_csv(here::here("code", "script", "dredge_best_auto.csv"))

# 
m_dredged1 <- lmer(AME_Z ~ Jobs + IncDiff + House + Stock + ChangeFlow + Stock*IncDiff + w2016 + orig13 +  eeurope + twowayfe + level_cyear + twowayfe*Jobs + cluster_any*gdp_ivC + (1 | team), data = cri_ml)

m_dredged2 <- lmer(AME_Z ~ Jobs + IncDiff + House + Stock + ChangeFlow + Stock*IncDiff + w2016 + orig13 +  eeurope + twowayfe + level_cyear + twowayfe*Jobs + ols*unbalpanel + (1 | team), data = cri_ml)

m_dredged3 <- lmer(AME_Z ~ Jobs + IncDiff + House + Stock + ChangeFlow + Stock*IncDiff + w2016 + orig13 +  eeurope + twowayfe + level_cyear + twowayfe*Jobs + Unemp*publice_iv + (1 | team), data = cri_ml)

m_dredged4 <- lmer(AME_Z ~ Jobs + IncDiff + House + Stock + ChangeFlow + Stock*IncDiff + w2016 + orig13 +  eeurope + twowayfe + level_cyear + twowayfe*Jobs + w1996*conservatism_ivC + (1 | team), data = cri_ml)

# from Main Analysis (for comparison)
m13 <- lmer(AME_Z ~ Jobs + IncDiff + House+ logit + ols + Stock + ChangeFlow+ w1996 + w2006 + w2016 + w2006*w2016 + orig13  + eeurope + allavailable + twowayfe + level_cyear+ total_score + (1 | team), data = cri_ml)

sjPlot::tab_model(m13,m_dredged,m_dredged1,m_dredged2,m_dredged3,m_dredged4, digits = 3, p.style = "stars", show.ci = F, show.loglik = T, show.aic = T, file = here::here("results/reg_dredge_v2.htm"))

sjPlot::tab_model(m13,m_dredged,m_dredged1,m_dredged2,m_dredged3,m_dredged4, digits = 3, p.style = "stars", show.ci = F, show.loglik = T, show.aic = T)

knitr::include_graphics(here::here("results","reg_dredge_v2.htm"))
```


```{r dredge_v2}
# in fact one variable increases the fit and explained variance (although itself is not sig), we updated our models accordingly.


sjPlot::tab_model(m_dredged,m_dredged3, digits = 3, p.style = "stars", show.ci = F, show.loglik = T, show.aic = T, file = here::here("results/reg_dredge_v2.htm"))

m_d_out_v <- as.data.frame(VarCorr(m_dredged))
m_d_out_v3 <- as.data.frame(VarCorr(m_dredged3))

m_d_out <- as.data.frame(read_html(here::here("results/reg_dredge_v2.htm")) %>% html_table(fill=TRUE))

m_d_out <- m_d_out[-c(21:24),]
m_d_out[c(18:20),1] <- c("Team-Level","Model-Level","Total")
# values taken from main models, see Table S6 (so total variance at each level in DV)
m_d_out[c(18:20),2] <- c(round((-1*(m_d_out_v[1,4]-0.000615)/0.000615)*100,3), 
                         round((-1*(m_d_out_v[2,4]-0.004882)/0.004882)*100,3), 
                         round((((-1*(m_d_out_v[1,4]-0.000615)) + (-1*(m_d_out_v[2,4]-0.004882)))/0.005497)*100,3))


m_d_out[c(18:20),3] <- c(round((-1*(m_d_out_v3[1,4]-0.000615)/0.000615)*100,3), 
                         round((-1*(m_d_out_v3[2,4]-0.004882)/0.004882)*100,3), 
                         round((((-1*(m_d_out_v3[1,4]-0.000615)) + (-1*(m_d_out_v3[2,4]-0.004882)))/0.005497)*100,3))




# Save table
write.csv(m_d_out, file = here::here("results/TblS10.csv"))

```


Computer selected model can explain `r m_d_out[18,2]` of the total variance.

## Colophon

This file is part of [https://github.com/nbreznau/CRI](https://github.com/nbreznau/CRI), the reproduction materials for [*Observing Many Researchers using the Same Data and Hypothesis Reveals a Hidden Universe of Uncertainty*](https://doi.org/10.31222/osf.io/cd5j9).

```{r colophon, echo=FALSE}
sessionInfo()
```
