---
title: "Tech 7. DV-Specific Analyses"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
library("pacman")

#necessary for nnet::multinom and tab_model to work together
# install.packages("devtools")
# devtools::install_github("easystats/insight")
# devtools::install_github("easystats/effectsize")

pacman::p_load("ggplot2","dplyr","readr","plotscale","lattice","tidyr","readxl","mlogit","jtools","sjPlot","sjmisc","sjlabelled","knitr","kableExtra","lavaan","reshape2","semPlot","lavaanPlot","leaps","lme4","multilevelTools","rvest","nnet","parameters","insight","effectsize","ggtext","mdthemes","ragg")

# add in variance estimates (more than 2-digits)
# disable scientific notation
options(scipen = 999)

# Column no missing function
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
```

## Data Prep

These datasets were worked up from the file 01_CRI_Data_Prep.Rmd. 

- `cri` = numerical values
- `cri_str` = string values
- `cri_team` = team-level data (by conclusion)
- `cri_team_combine` = team-level data parsed by type of test variable (stock and flow)
- `cri_indiv` = participant-level data from our survey, identifying characteristics redacted

### Load Data

```{r load, warning=FALSE,message=FALSE}
cri <- read.csv(file = here::here("data/cri.csv"), header = TRUE)
cri_str <- read.csv(file = here::here("data/cri_str.csv"), header = TRUE)
cri_indiv <- read.csv(file = here::here("data/cri_indv.csv"), header = TRUE)

# setup multilevel dataset

cri_ml <- select(cri,u_teamid, id, u_delibtreatmentgroup1, AME:main_IV_source, main_IV_measurement:package, countries, Jobs:anynonlin,AME_Z,lower_Z,upper_Z,Hsup,Hrej,Hno,AME_sup_p05:AME_ns_p05,u_expgroup1,belief_strength:belief_ipred, HresultF, STATISTICS_SKILL, BELIEF_HYPOTHESIS, TOPIC_KNOWLEDGE, MODEL_SCORE, PRO_IMMIGRANT)

# create a team ID variable to identify the independent tests by team. Again, 16 of 71 teams had independent conclusions - seeing stock v flow immigration measures as representative of independent tests of the hypothesis. Therefore, we have a team-test level that replaces the team level.

cri_ml$team <- cri_ml %>% group_indices(u_teamid, HresultF)

cri_ml <- select(cri_ml, u_teamid, id, team, AME_Z, upper_Z, lower_Z, everything())

# remove team 0
cri_ml <- subset(cri_ml, u_teamid != 0)
```

### Within and Between Variables

```{r wandb, warning = FALSE, message = FALSE}
cri_ml <- cri_ml %>%
  group_by(team) %>%
  mutate(AME_Z_b = mean(AME_Z, na.rm = TRUE),
         AME_Z_w =AME_Z-AME_Z_b,
         jobs_b = mean(Jobs, na.rm = TRUE),
         unemp_b = mean(Unemp, na.rm = TRUE),
         incdiff_b = mean(IncDiff, na.rm = TRUE),
         oldage_b = mean(OldAge, na.rm = TRUE),
         house_b = mean(House, na.rm = TRUE),
         health_b = mean(Health, na.rm = TRUE),
         jobs_w = Jobs-jobs_b,
         unemp_w = Unemp-unemp_b,
         incdiff_w = IncDiff-incdiff_b,
         oldage_w = OldAge-oldage_b,
         house_w = House-house_b,
         health_w = Health-health_b,
         scale_b = mean(Scale, na.rm = TRUE),
         scale_w = Scale-scale_b,
         un_emp_rate_ivC = ifelse(emplrate_ivC == 1 | unemprate_ivC == 1, 1, 0)) %>%
  ungroup()

# create factors for measurement
cri_ml <- cri_ml %>%
  mutate(main_IV_factor = as.factor(main_IV_measurement))

# team 27 is missing the survey variables
# as it is just one team, mean replacement should be fine
cri_ml <- cri_ml %>%
  mutate(stats_ipred = ifelse(is.na(stats_ipred), mean(stats_ipred, na.rm=T), stats_ipred),
         belief_ipred = ifelse(is.na(belief_ipred), mean(belief_ipred, na.rm =T), belief_ipred),
         topic_ipred = ifelse(is.na(topic_ipred), mean(topic_ipred, na.rm =T), topic_ipred))

# split data by DV
cri_ml_jobs <- subset(cri_ml, Jobs == 1 & Scale != 1)
cri_ml_oldage <- subset(cri_ml, OldAge == 1 & Scale != 1)
cri_ml_incdiff <- subset(cri_ml, IncDiff == 1 & Scale != 1)
cri_ml_unemp <- subset(cri_ml, Unemp == 1 & Scale != 1)
cri_ml_house <- subset(cri_ml, House == 1 & Scale != 1)
cri_ml_health <- subset(cri_ml, Health == 1 & Scale != 1)
```

## Regresssion Approach to Explaining Variance by DV

### Explaining Average Marginal Effects

#### Objective Conditions

Here we consider re-run our main analyses independently by DV.

#### Subjective Decisions

##### Measurement

The teams had several possibilities to measure the DV (or DVs) including linear, logit or multinomial. Also, immigration could be stock or flow and some teams elected for change in flow. A few teams used measures like refugee or non-western instead of simply foreign-born. These decisions are reflected here.

note that logit is the only one that seems to matter, surprisingly the 'type' of measure does not matter (foreign-born, non-western, refugee, etc.; although there are far fewer models that do not simply use foreign-born)

In the DV specific case there is often only one model per team, thus the multilevel structure is not helpful (mostly singular identification as a result). Therefore we switch to an lm (results are nearly identical because the random-intercepts at the team-level were zero)

```{r subj_measurement_mlms, warning = FALSE, message = FALSE}

dvs <- c("Jobs","Unemp","IncDiff","OldAge","House","Health")
#run regressions across all datasets

m03_dv <- lapply(list(cri_ml_jobs, cri_ml_unemp, cri_ml_incdiff, cri_ml_oldage, cri_ml_house, cri_ml_health), lm, formula = AME_Z ~ logit + ologit + lpm + mlogit + ols)

m04_dv <- lapply(list(cri_ml_jobs, cri_ml_unemp, cri_ml_incdiff, cri_ml_oldage, cri_ml_house, cri_ml_health), lm, formula = AME_Z ~ logit + ols + Stock + ChangeFlow)

# extract variance
# make frame
dv_var_table <- as.data.frame(matrix(nrow = 31, ncol = 6))

sum_adjr <- function(x,y) round(summary(x[[y]])[["adj.r.squared"]],3)
sum_r <- function(x,y) round(summary(x[[y]])[["r.squared"]],3)
sum_cases <- function(x,y) nobs(x[[y]])

# m03 - same naming convention as main analyses
dv_var_table[1,1:6] <- c("Model","DV","Specs","r2","adj_r2","Cases")
dv_var_table[2:7,1] <- "m03"
dv_var_table[2:7,2] <- dvs
dv_var_table[2:7,3] <- rep("~ logit + ologit + lpm + mlogit + ols",6)
dv_var_table[2:7,4] <- c(sum_r(m03_dv,1),sum_r(m03_dv,2),sum_r(m03_dv,3),sum_r(m03_dv,4),sum_r(m03_dv,5),sum_r(m03_dv,6))
dv_var_table[2:7,5] <- c(sum_adjr(m03_dv,1),sum_adjr(m03_dv,2),sum_adjr(m03_dv,3),sum_adjr(m03_dv,4),sum_adjr(m03_dv,5),sum_adjr(m03_dv,6))
dv_var_table[2:7,6] <- c(sum_cases(m03_dv,1),sum_cases(m03_dv,2),sum_cases(m03_dv,3),sum_cases(m03_dv,4),sum_cases(m03_dv,5),sum_cases(m03_dv,6))

# m04 

dv_var_table[8:13,1] <- "m04"
dv_var_table[8:13,2] <- dvs
dv_var_table[8:13,3] <- rep("~ logit + ols + Stock + ChangeFlow",6)
dv_var_table[8:13,4] <- c(sum_r(m04_dv,1),sum_r(m04_dv,2),sum_r(m04_dv,3),sum_r(m04_dv,4),sum_r(m04_dv,5),sum_r(m04_dv,6))
dv_var_table[8:13,5] <- c(sum_adjr(m04_dv,1),sum_adjr(m04_dv,2),sum_adjr(m04_dv,3),sum_adjr(m04_dv,4),sum_adjr(m04_dv,5),sum_adjr(m04_dv,6))
dv_var_table[8:13,6] <- c(sum_cases(m04_dv,1),sum_cases(m04_dv,2),sum_cases(m04_dv,3),sum_cases(m04_dv,4),sum_cases(m04_dv,5),sum_cases(m04_dv,6))
```

##### Data and Sample

```{r subj_datasamp_mlms, warning = FALSE}
# m05_dv <- lapply(list(cri_ml_jobs, cri_ml_unemp, cri_ml_incdiff, cri_ml_oldage, cri_ml_house, cri_ml_health), lm, formula = AME_Z ~ logit + ols + Stock + ChangeFlow)

m06_dv <- lapply(list(cri_ml_jobs, cri_ml_unemp, cri_ml_incdiff, cri_ml_oldage, cri_ml_house, cri_ml_health), lm, formula = AME_Z ~ logit + ols + Stock + ChangeFlow + w1996 + w2006 + w2016 + w2006*w2016 + orig13  + eeurope + allavailable)

dv_var_table[14:19,1] <- "m06"
dv_var_table[14:19,2] <- dvs
dv_var_table[14:19,3] <- rep("~ logit + ols + Stock + ChangeFlow + w1996 + w2006 + w2016 + w2006*w2016 + orig13  + eeurope + allavailable",6)
dv_var_table[14:19,4] <- c(sum_r(m06_dv,1),sum_r(m06_dv,2),sum_r(m06_dv,3),sum_r(m06_dv,4),sum_r(m06_dv,5),sum_r(m06_dv,6))
dv_var_table[14:19,5] <- c(sum_adjr(m06_dv,1),sum_adjr(m06_dv,2),sum_adjr(m06_dv,3),sum_adjr(m06_dv,4),sum_adjr(m06_dv,5),sum_adjr(m06_dv,6))
dv_var_table[14:19,6] <- c(sum_cases(m06_dv,1),sum_cases(m06_dv,2),sum_cases(m06_dv,3),sum_cases(m06_dv,4),sum_cases(m06_dv,5),sum_cases(m06_dv,6))
```

##### Model Design

Given such fewer cases we adjust the number of variables.

```{r subj_model_mlms, warning = FALSE, message = FALSE}
m08_dv <- lapply(list(cri_ml_jobs, cri_ml_unemp, cri_ml_incdiff, cri_ml_oldage, cri_ml_house, cri_ml_health), lm, formula = AME_Z ~ logit + ols + Stock + ChangeFlow + twowayfe + mlm_fe + level_cyear  + mlm_re  + gdp_ivC + anynonlin)

dv_var_table[20:25,1] <- "m08x"
dv_var_table[20:25,2] <- dvs
dv_var_table[20:25,3] <- rep("~ logit + ols + Stock + ChangeFlow + twowayfe + mlm_fe + mlm_re  + gdp_ivC + anynonlin",6)
dv_var_table[20:25,4] <- c(sum_r(m08_dv,1),sum_r(m08_dv,2),sum_r(m08_dv,3),sum_r(m08_dv,4),sum_r(m08_dv,5),sum_r(m08_dv,6))
dv_var_table[20:25,5] <- c(sum_adjr(m08_dv,1),sum_adjr(m08_dv,2),sum_adjr(m08_dv,3),sum_adjr(m08_dv,4),sum_adjr(m08_dv,5),sum_adjr(m08_dv,6))
dv_var_table[20:25,6] <- c(sum_cases(m08_dv,1),sum_cases(m08_dv,2),sum_cases(m08_dv,3),sum_cases(m08_dv,4),sum_cases(m08_dv,5),sum_cases(m08_dv,6))
```

#### Researcher Aspects

- `belief_ipred` - Belief that Hypothesis is true (that immigration reduces support), team average of predicted factor scores
- `pro_immigrant` - Support laws to better integrate immigrants, team average, single question
- `topic_ipred` - Knowledge and experience with the topic of immigration and welfare state preferences, team average of predicted factor scores
- `stats_ipred` - Knowledge and experience with quantiative statistical analysis, team average of predicted factor scores
- `total_score` - Average score of each model from subjective voting amongst participants, each participant reviewed 3 to 4 models

##### Maximum variance explained

Again we use a modified version, dropping many variables from m08x.

```{r res_aspects_mlms, warning = FALSE, message = FALSE}
m12_dv <- lapply(list(cri_ml_jobs, cri_ml_unemp, cri_ml_incdiff, cri_ml_oldage, cri_ml_house, cri_ml_health), lm, formula = AME_Z ~ logit + ols + Stock + ChangeFlow + twowayfe + mlm_fe + belief_ipred + pro_immigrant + stats_ipred + topic_ipred + total_score)

dv_var_table[26:31,1] <- "m12x"
dv_var_table[26:31,2] <- dvs
dv_var_table[26:31,3] <- rep("~ logit + ols + Stock + ChangeFlow + twowayfe + mlm_fe + belief_ipred + pro_immigrant + stats_ipred + topic_ipred + total_score",6)
dv_var_table[26:31,4] <- c(sum_r(m12_dv,1),sum_r(m12_dv,2),sum_r(m12_dv,3),sum_r(m12_dv,4),sum_r(m12_dv,5),sum_r(m12_dv,6))
dv_var_table[26:31,5] <- c(sum_adjr(m12_dv,1),sum_adjr(m12_dv,2),sum_adjr(m12_dv,3),sum_adjr(m12_dv,4),sum_adjr(m12_dv,5),sum_adjr(m12_dv,6))
dv_var_table[26:31,6] <- c(sum_cases(m12_dv,1),sum_cases(m12_dv,2),sum_cases(m12_dv,3),sum_cases(m12_dv,4),sum_cases(m12_dv,5),sum_cases(m12_dv,6))
```

##### Save as table

```{r output}
write.csv(dv_var_table, file = here::here("results/TblS9.csv"))
```

## Colophon

This file is part of [https://github.com/nbreznau/CRI](https://github.com/nbreznau/CRI), the reproduction materials for [*Observing Many Researchers using the Same Data and Hypothesis Reveals a Hidden Universe of Uncertainty*](https://osf.io/preprints/metaarxiv/cd5j9/).

```{r colophon, echo=FALSE}
sessionInfo()
```